Lesson 3
========================================================

***

### What to Do First?
Notes:

***

### Pseudo-Facebook User Data
Notes:

```{r Pseudo-Facebook User Data}

```

***

### Histogram of Users' Birthdays
Notes:

```{r Histogram of Users\' Birthdays}
#install.packages('ggplot2')
library(ggplot2)

#install.packages("gridExtra")
library(gridExtra)

qplot(x = dob_day, data = pf)
# scale_x_continuous(breaks = 1:31)
```

***

#### What are some things that you notice about this histogram?
Response:

The scale_x_discrete() function throws an error in my console. The 
histogram is very skewed toward the first day of the month.
***

### Moira's Investigation
Notes:

***

### Estimating Your Audience Size
Notes:

***

#### Think about a time when you posted a specific message or shared a photo on Facebook. What was it?
Response:

#### How many of your friends do you think saw that post?
Response:

#### Think about what percent of your friends on Facebook see any posts or comments that you make in a month. What percent do you think that is?
Response:

***

### Perceived Audience Size
Notes:

***
### Faceting
Notes:

```{r Faceting}
qplot(x = dob_day, data = pf) +
	facet_wrap(~dob_month, ncol = 3)
```

#### Let’s take another look at our plot. What stands out to you here?
Response:

There is a disproportionate number of people born on January 1st.
***

### Be Skeptical - Outliers and Anomalies
Notes:

***

### Moira's Outlier
Notes:
#### Which case do you think applies to Moira’s outlier?
Response:

***

### Friend Count
Notes:

#### What code would you enter to create a histogram of friend counts?

```{r Friend Count}

```

#### How is this plot similar to Moira's first plot?
Response:

***

### Limiting the Axes
Notes:
The xlim parameter will truncate everything larger than the upper bound.

```{r Limiting the Axes}
qplot(x = friend_count, data = pf, xlim = c(0, 1000))

qplot(x = friend_count, data = pf, xlim = c(0, 1000)) +
	scale_x_continuous(limits = c(0, 1000))
```

### Exploring with Bin Width
Notes:
Bin width governs the width of the bars in a histogram.
***

### Adjusting the Bin Width
Notes:

### Faceting Friend Count
```{r Faceting Friend Count}
# What code would you add to create a facet the histogram by gender?
# Add it to the code below.
qplot(x = friend_count, data = pf, binwidth = 10) +
  scale_x_continuous(limits = c(0, 1000),
                     breaks = seq(0, 1000, 50))
```

***

### Omitting NA Values
Notes:
You can use na.omit() to omit all rows with NA values in a column
```{r Omitting NA Values}

```

***

### Statistics 'by' Gender
Notes:

```{r Statistics \'by\' Gender}
by(pf$friend_count, pf$gender, summary)
```

#### Who on average has more friends: men or women?
Response:
Women

#### What's the difference between the median friend count for women and men?
Response:
'r 96-74'

#### Why would the median be a better measure than the mean?
Response:
The data has a long-tail format, which means that the very few outliers with
huge friend counts would skew the mean much higher than it should be.
***

### Tenure
Notes:

```{r Tenure}
qplot(x = tenure, data = pf, color = I("black"), fill = I("#8C70C9"))
```

***

#### How would you create a histogram of tenure by year?

```{r Tenure Histogram by Year}
qplot(x = tenure/365, data = pf, binwidth = 1, color = I("black"), fill = I("#8C70C9"))
```

***

### Labeling Plots
Notes:
Just use the xlab/ylab parameters

```{r Labeling Plots}
qplot(x = tenure/365, data = pf, binwidth = 1,
			xlab = "Number of years using Facebook",
			ylab = "Number of users",
			color = I("black"), fill = I("#8C70C9"))
```

***

### User Ages
Notes:

```{r User Ages}
qplot(x = age, data = pf, binwidth = 1, color = I("black"), fill = I("#8C70C9")) +
	scale_x_continuous(breaks = seq(0, 150, by = 5))
```

#### What do you notice?
Response:
There is a large number of outliers at the high end of the spectrum
that are skewing the data. The vast majority of users are concentrated around
the 10-30 mark, which is intuitive given Facebook's target audience.
***

### The Spread of Memes
Notes:
Using logarithms, data can be normalized to decrease the impact
of over-dispersion. Log(0) is undefined, so add one to values
that might be zero. Log10 basically transforms data into orders
of magnitude instead of absolute values.
***

### Lada's Money Bag Meme
Notes:

***

### Transforming Data
Notes:

***

```{r Logarithm of Friend Count}
#no_scale <- qplot(x = friend_count+1, data = pf, binwidth = 50, color = I("black"), fill = I("#8C70C9"))
#log10_scale <- qplot(x = log10(friend_count+1), data = pf, binwidth = 0.2, color = I("black"), fill = I("#8C70C9"))
#sqrt_scale <- qplot(x = sqrt(friend_count+1), data = pf, binwidth = 50, color = I("black"), fill = I("#8C70C9"))

# This is better because the friendly labeling of the x axis is more readable. 
# log10 will label the axis with actual values instead of log units.
no_scale <- ggplot(aes(x = friend_count), data = pf) + geom_histogram()
log10_scale <- no_scale + scale_x_log10()
sqrt_scale <- no_scale + scale_x_sqrt()

grid.arrange(no_scale, log10_scale, sqrt_scale, ncol = 1)
```

### Add a Scaling Layer
Notes:

```{r Add a Scaling Layer}

```

***


### Frequency Polygons

```{r Frequency Polygons}
#qplot(x = log10(likes), 
#		data = subset(pf, !is.na(gender)), 
#		xlab = "Likes", 
#		ylab = "Number of Users", 
#		binwidth = 500, 
#		geom = "freqpoly") + 
#	facet_wrap(~gender)
#	scale_x_log10()

qplot(x = likes,
		data = subset(pf, !is.na(gender)),
		geom = "freqpoly",
		color = gender) +
	scale_x_continuous() +
	scale_x_log10()
```

***

### Likes on the Web
Notes:

```{r Likes on the Web}
by(pf$likes, pf$gender, sum)
```


***

### Box Plots
Notes:

```{r Box Plots}
qplot(x = gender,
		y = friend_count,
		data = subset(pf, !is.na(gender)),
		geom = "boxplot") +
	facet_wrap(~gender)
```

#### Adjust the code to focus on users who have friend counts between 0 and 1000.

```{r}
qplot(x = gender,
		y = friend_count,
		data = subset(pf, !is.na(gender)),
		geom = "boxplot") +
	scale_y_continuous(limits = c(0, 1000)) +
	facet_wrap(~gender)
```

***

### Box Plots, Quartiles, and Friendships
Notes:
coord_cartesian() is better for setting the y limits. scale_y_continuous()
changes the actual values displayed.

```{r Box Plots, Quartiles, and Friendships}
by(pf$friendships_initiated, pf$gender, summary)
qplot(x = gender,
		y = friendships_initiated,
		data = subset(pf, !is.na(gender)),
		geom = "boxplot") +
	coord_cartesian(ylim = c(0, 100)) +
	facet_wrap(~gender)
```

#### On average, who initiated more friendships in our sample: men or women?
Response:
#### Write about some ways that you can verify your answer.
Response:
```{r Friend Requests by Gender}

```

Response:

***

### Getting Logical
Notes:

```{r Getting Logical}

```

Response:

***

### Analyzing One Variable
Reflection:

***

Click **KnitHTML** to see all of your hard work and to have an html
page of this lesson, your answers, and your notes!